### 2020-07-22 text/content.tex
Correct typos and table notes.
Resolves #16

To study how the patterns of interaction have changed in the U.S. during the Covid-19 pandemic, we use customer mobility data from SafeGraph \cite{SafeGraph2020-gn}. This dataset measures the number of visits to a business in a given month, as captured from several cell phone apps and made available to researchers in an anonymized form. We study how the reduced number of customer vists is correlated with changes in sectoral employment.

@@

\section*{Results}
Table \ref{table2} displays the top five and the bottom five industries by 2-digit NAICS industries as sorted by the percentage of workers in communication-intensive occupations, excluding hospitals and clinics. Across industries, retail trade, accommodation and food services, arts, entertainment, and recreation, other services and administrative and support and waste management and remediation services have the highest share of communication-intensive workers, exceeding 35 percent. Information, transportation, production, professional, scientific, and technical Services and agricultural industries are less reliant on face-to-face communication. This heterogeneity across industries is important to understand the effect of social distancing measures.

@@

As we see from the regression results above, the largest decline in sectoral employment are in sectors where the share of customer-facing workers is highest. We hence use the share of customer-facing workers for the following analysis.

@@

\hline
\end{tabular}
\begin{flushleft} ``Wage subsidy'' displays the percentage decrease in labor costs necessary to compensate businesses when worker contacts are reduced by half. ``Employment'' is the February 2020 employment of the sector in thousands \cite{CES}. The last row shows the employment-weighted average wage subsidy. Table excludes hospitals, clinics, and government establishments which are not present in CBP.
\end{flushleft}
\label{table3}
%\end{adjustwidth}
\end{table}

>>>>

To study how the patterns of interaction have changed in the U.S. during the Covid-19 pandemic, we use customer mobility data from SafeGraph \cite{SafeGraph2020-gn}. This dataset measures the number of visits to a business in a given month, as captured from several cell phone apps and made available to researchers in an anonymized form. We study how the reduced number of customer visits is correlated with changes in sectoral employment.

@@

\section*{Results}
Table \ref{table2} displays the top five and the bottom five industries by 2-digit NAICS industries as sorted by the percentage of workers in communication-intensive occupations, excluding hospitals and clinics. Across industries, retail trade and accommodation and food services, arts, entertainment, and recreation have the highest share of communication-intensive workers, exceeding 35 percent. Information, transportation, production, professional, scientific, and technical Services and agricultural industries are less reliant on face-to-face communication. This heterogeneity across industries is important to understand the effect of social distancing measures.

@@

As we see from the regression results above, the largest decline in sectoral employment is in sectors where the share of customer-facing workers is highest. We hence use the share of customer-facing workers for the following analysis.

@@

\hline
\end{tabular}
\begin{flushleft} ``Wage subsidy'' displays the percentage decrease in labor costs necessary to compensate businesses for the reduced number of customer-worker contacts. ``Employment'' is the February 2020 employment of the sector in thousands \cite{CES}. The last row shows the employment-weighted average wage subsidy. Table excludes hospitals, clinics, and government establishments which are not present in CBP.
\end{flushleft}
\label{table3}
%\end{adjustwidth}
\end{table}
